Will Kamala Harris will win the 2024 Presidential election

### 2024-11-04 paper/paper.qmd
.

---
title: "Will Kamala Harris will win the 2024 Presidential election"
subtitle: "Analysing the polls using baysian modeling"
author: 
  - Yan Mezhiborsky
  - Cristina Burca
  - Shreya Sakura Noskor
thanks: "Code and data are available at: [https://github.com/Mezhi18/US_Election2024.git](https://github.com/Mezhi18/US_Election2024.git)."
date: today
date-format: long
abstract: "We analyse the probability of Kamala Harris winning in the 7 swing states of USA using baysian modeling;the states we look at are Arizona, Michigan, Pennsylvania, Nevada, Georgia, Wisconsin and North Carolina. USA is a large country with its national economy affecting the global economic conditions, which is why predicting the future President of USA will help understand the future economic condiotion of the world. Through baysian modelling we found that North Carolina (47.26% support for Harris), Nevada(46.43% support for Harris), Wisconsin(48.38% support for Harris), Michigan(47.30% support for Harris), Pennsylvania(48.02% support for Harris) will vote Kamala Harris, while the rest of the swing states might vote Donald Trump, meaning that majority of the swing states will vote Kamala Harris. Provided this we predict that Kamal Harris will win the election. By creating a baysian model based on 'polls of 'polls'  where we compare the results from different polls, we are able to make this prediction."
format:
  pdf:
    bibliography: references.bib
    documentclass: article
    geometry: margin = 1in
number-sections: true
toc: true
bibliography: references.bib
---

>>>>

---
title: "Will Kamala Harris will win the 2024 Presidential election"
subtitle: "Analysing the polls using baysian modeling"
author: 
  - Yan Mezhiborsky
  - Cristina Burca
  - Shreya Sakura Noskor
thanks: "Code and data are available at: [https://github.com/Mezhi18/US_Election2024.git](https://github.com/Mezhi18/US_Election2024.git)."
date: today
date-format: long
abstract: "We analyse the probability of Kamala Harris winning in the 7 swing states of USA using baysian modeling;the states we look at are Arizona, Michigan, Pennsylvania, Nevada, Georgia, Wisconsin and North Carolina. USA is a large country with its national economy affecting the global economic conditions, which is why predicting the future President of USA will help understand the future economic condiotion of the world. Through baysian modelling we found that North Carolina (47.26% support for Harris), Nevada(46.43% support for Harris), Wisconsin(48.38% support for Harris), Michigan(47.30% support for Harris), Pennsylvania(48.02% support for Harris) will vote Kamala Harris, while the rest of the swing states might vote Donald Trump, meaning that majority of the swing states will vote Kamala Harris. Provided this we predict that Kamal Harris will win the election. By creating a baysian model based on 'polls of polls'  where we compare the results from different polls, we are able to make this prediction."
format:
  pdf:
    bibliography: references.bib
    documentclass: article
    geometry: margin = 1in
number-sections: true
toc: true
bibliography: references.bib
---
